%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{ٰVahid Etemadi} % Your name
\address{Shiraz University of Technology, Shiraz, Iran} % Your address
\address{v.etemadi@sutech.ac.ir; +98-936-543-3074}
\address{\url{http://vahidetemadi.github.io} }

\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\rfoot{ \hfill Page \thepage \hspace{1pt} of \pageref{LastPage}}
 

\begin{document}

\begin{rSection}{Research Interests}
Software engineering, Software socio-technical analysis, Empirical software engineering, Artificial intelligence, Search-based software engineering, Machine learning
\end{rSection}

% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
	{\bf Shiraz University of Technology, Shiraz, Iran } \hfill {\em Aug 2014 - Sep 2021}\\
	Ph.D. in Information Technology, Software Engineering and Distributed Systems Lab, Department of Computer Science and IT.\\
	Thesis: Software Change Management as A Service: A Self-Adaptive Approach\\
	\\{\bf K. N. Toosi University of Technology (KNTU), Tehran, Iran } \hfill {\em Aug 2012 - Aug 2014} 
	\\ M.Sc. in  Management Information Systems, Data Mining Group, Department of Industrial Engineering.\\
	Thesis: Improving Recommendation Systems in Social Networks Using Profile Mining\\
	\\{\bf Shiraz University of Technology, Shiraz, Iran } \hfill {\em Aug 2008 - Aug 2012} 
	\\ B.Sc. in Information Technology Engineering, Department of Computer Engineering and IT.\\
	Thesis: Content and Service Distribution over Cloud Computing Environments
	
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}
{\bf Graduate Researcher at Distributed Systems Lab, \href{https://sutech.ac.ir/en} {Shiraz University of Technology} Shiraz, Iran} \hfill {\em  Aug 2014 - Sep 2021}\\
Making software maintenance more automated through focusing on bug locating and task assignment.\\
Providing a scheduling-driven approach to minimize the \emph{Time} and the \emph{Cost} in bug fixing assignments during maintaining software.\\
Involving \emph{Knowledge Diffusion} as the key objective during fixing task assignment for making development team more robust to developer churn (increasing sustainability).\\

{\bf Internship in Open Source Software Engineering at \href{https://fstp.ir} {Pajouhan Matin}, Shiraz Technological Park, Shiraz, Iran} \hfill {\em Aug 2019 - Dec 2019}\\
Contributing to open source software such as mxGraph to make it a fit for BPMN systems.
\\Requirement modeling in UML notation using Visual Paradigm tools.
\\Adopting software design patterns for machine learning applications.

{\bf Visiting Researcher at \href{https://urjc.es} {Universidad Rey Juan Carlos}, Madrid, Spain} \hfill {\em Apr 2018 - Dec 2018} 
\\Visiting LibreSoft lab at the Department of Telecommunication Engineering under the supervision of Prof. Gregorio Robles and Prof. Jesús M. González-Barahona.

{\bf Software Engineer at \href{https://asretelecom.net}{AsreTelecom}, Shiraz Branch, Shiraz, Iran} \hfill {\em Sep 2015 - Oct 2017} 
\\  Developing and maintaining MS SQL server databases, implementing the main process which take place inside ASAN Internet Service Provider company, designing and implementing reporting dashboards.\\
\\{\bf Graduate Researcher at \href{https://www.kntu.ac.ir/Index.aspx?lang=2\&sub=73} {IE-Data Mining Group} K. N. Toosi University of Technology, Tehran, Iran} \hfill {\em Sep 2012 - Sep 2014}\\
Working on a sample network retrieved from \emph{Facebook.com} to propose a hybrid friend recommendation system.
% \\{\bf Software Developer at Saamaneh Negar Paytakht, Tehran, Iran} \hfill {\em Sep 2010 - Mar 2012} 
% \\ Developed and maintained an Electronic Health Records software. \\


\end{rSection}


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Publications}

\item \textbf{Etemadi, V.}, Gonzalez-Barahona, Jesus M., Robles, G., 2021. \emph{I want to invest in an OSS project: Shall I hire Insiders or Outsiders?}, Accepted for presentation in BENEVOL 2021
\item \textbf{Etemadi, V.}, Bushehrian, O. and Robles, G., 2021. \emph{Task assignment to counter the effect of developer turnover in software maintenance: A knowledge diffusion model}. Information and Software Technology, 143, p.106786.
\item \textbf{Etemadi, V.}, Bushehrian, O., Akbari, R. and Robles, G., 2021. \emph{A scheduling-driven approach to efficiently assign bug fixing tasks to developers}. Journal of Systems and Software, 178, p.110967.
\item \textbf{Etemadi, V.}, Bushehrian, O. and Akbari, R.:  \textit{Association rule mining for finding usability problem patterns: A case study on StackOverflow}, In 2017 International Symposium on Computer Science and Software Engineering Conference (CSSE), pp. 24-29. IEEE, 2017
\item Emami, M., \textbf{Etemadi, V.}, Bushehrian, O. \textit{A component-based content distribution network architecture in cloud environments.} In 2015 2nd International Conference on Knowledge-Based Engineering and Innovation (KBEI), pp. 330-335. IEEE, 2015.\\

\end{rSection}



%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Reviewer/Services}
\item MSR hackathon (PC member) \hfill {\em  2021}
\item SQJO: Software Quality Journal, Springer \hfill {\em  2021}
\item ISTE: Iranian Journal of Science and Technology, Transactions of Electrical Engineering \hfill {\em  2019} 
\end{rSection}

\begin{rSection}{Teaching}
{\bf Lecturer,}{ Faculty of Electronic Learning, Shiraz University, Shiraz, Iran} \hfill {\em 2019} 
\\ Course: Advanced Programming in JAVA\\
{\bf Teaching Assistant,}{ Shiraz University of Technology, Shiraz, Iran} \hfill {\em  2019} 
\\ Course: Computer Architecture
\\{\bf Instructor,}{ Shiraz University of Technology, Shiraz, Iran} \hfill {\em 2016 - 2017} 
\\ Course: Database Systems Lab
\\{\bf Lecturer,}{ Faculty of Electronic Learning, Shiraz University, Shiraz, Iran} \hfill {\em 2016 - 2017} 
\\ Course: Multimedia Systems
\\{\bf Teaching Assistant,}{ Shiraz University of Technology, Shiraz, Iran} \hfill {\em 2015 - 2016} 
\\ Course: Software Engineering

\end{rSection}

%---------------------------------------------------------------------------
% Awards and Honors
%---------------------------------------------------------------------------
\begin{rSection}{Awards and Honors}
\item Student volunteer at 43th International Conference on Software Engineering (ICSE), Madrid, Spain  \hfill {\em  2021}
\item Graduate Research Assistant, Shiraz University of Technology \hfill {\em 2014 - 2021}
\item Won the travel grant for visiting LibreSoft research group in the Department of Telecommunication Engineering at URJC, Madrid, Spain (2018)
\item Student volunteer at 34th International Conference on Software Maintenance (ICSME), Madrid, Spain  \hfill {\em  2018}
\item Travel Grant from \href{https://www.bitergia.com} {Bitergia} to attend 11th Seminar on Advanced Techniques \& Tools for Software Evolution (SATToSE) \hfill {\em  2018}
\item Full tuition waiver scholarships for full time master of science students, K. N. Toosi University of Technology. \hfill {\em  2012 - 2014}
\item Full tuition waiver scholarships for full time undergraduate students, Shiraz University of Technology. \hfill {\em  2008 - 2012}
\item Ranked top 2\% nationwide university entrance exam for Bachelor of Science among more than 300,000. \hfill {\em  2008}

\end{rSection}
% ------------------------------------------------------------------------------------------
% Formal Presentation
% ------------------------------------------------------------------------------------------
\begin{rSection}{Presentations}
{\bf Fourth Madrilenian Seminar on Software Research (MADSESE), Universidad Alcalá de Henares, Spain} \hfill {\em May 9th 2018} 
\\ Title: Software Change Management as A Service: A Self-Adaptive Approach\\
{\bf 11th Seminar on Advanced Techniques \& Tools for Software Evolution - (SATToSE 2018), Athens, Greek} \hfill {\em June 2018}
\\ Presented in open MIC 
\\ Title: Self-Adaptive Software Maintenance\\

\end{rSection}

% ------------------------------------------------------------------------------------------
% Sample courses accomplished
% ------------------------------------------------------------------------------------------
\begin{rSection}{Sample Courses (Accomplished)}
	{\bf Advanced Distributed Systems} \\
	{\bf Semantic Web} \\
	{\bf Artificial Intelligence} \\
	{\bf Data Mining} \\
	{\bf Software Development Management } \\
%	{\bf Software Engineering I \& II } \\
	{\bf Database Systems } \\
	{\bf Algorithms Design } \\
	{\bf Software Testing} 
	
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Certificates}
	
	{\bf Social Network Analysis} \hfill {\em DEC 2013}
	\\Grade Achieved: 78.9\%
	\\Instructor: Prof. Lada Adamic
	\\Delivered by Coursera.org
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Proficiency}

{\bf Back-end:}  {\em Advanced Knowledge of JavaSE, Spring boot, Experience with Python and C\#,  Familiar with Scala, PHP, Nodes.js} \\
{\bf Front end:}  {\em   JavaScript, HTML, CSS, Familiar with Vue.js}\\
{\bf CI/CD:}  {\em  Docker, Experience with Jenkins, Knowledge of GitHub action}\\
{\bf Web-Service:}  {\em  Experience with REST, Familiar with SOA, GraphQL}\\
{\bf Database:}  {\em Microsoft SQL, MySQL, PostgerSQL, Familiar with Elasticsearch, Firebase}\\
{\bf Software Design (\&Tools):}  {\em Object-Oriented Design, UML, Visual Paradigm, UML Rational Rose}\\
{\bf Test:}  {\em Defect and Bug Discovery, JUnit, Mockito}\\
{\bf Version control:}  {\em Git, Team foundation server}\\
{\bf Analytical Tools:}  {\em Weka, Gephi}\\
{\bf ML:}  {\em Familiar with PyTorch}\\
{\bf Semantic-analysis:}  {\em  Knowledge of OWL, RDF, XML, Familiar with Apache Jena, Protégé}\\
{\bf Operating systems:}  {\em Linux, Windows}\\
{\bf Big data:}  {\em Apache Spark}\\


\end{rSection}
% % ------------------------------------------------------------------------------------------
% % Referres
% % ------------------------------------------------------------------------------------------
\begin{rSection}{References}
	Available upon request.
%	Prof. Gregorio Robles, Full Professor at Universidad Rey Juan Carlos, Madrid, Spain\\
%	Contact: grex@gsyc.urjc.es\\	
%	Dr. Omid Bushehrian, Associate Professor at Shiraz University of Technology, Shiraz, Iran\\
%	Contact: bushehrian@sutech.ac.ir\\
%	Dr. Reza Akbari, Associate Professor at Shiraz University of Technology, Shiraz, Iran\\
%	Contact: akbari@sutech.ac.ir
	
%	Dr. Reza Akbari, Associate Professor at Shiraz University of Technology, Shiraz, Iran\\
%	Contact: akbari@sutech.ac.ir\\
	
%	Dr. Mostafa Fakhrahmad, Assistant Professor at Shiraz University, Shiraz, Iran\\
%	Contact: fakhrahmad@shirazu.ac.ir
%	Dr. Mohsen Emami, Senior Researcher at Uppsala University, Uppsala, Sweden\\
%	Contact: emami.mohsen@gmail.com\\
	
\end{rSection}


\end{document}

